---
title: "Global meta-analysis reveals positive effects of sugar provisioning on parasitoids in agroecosystems, without conclusive evidence for reduced pest densities"
subtitle: "Appendix S3 - Posthoc analyses"
author: "Martin Luquet, Blas Lavandero, Emmanuel Desouhant, Bruno Jaloux"
date: "`r format(Sys.time(), '%Y/%m/%d')` - first created on 2026/02/03"
output: pdf_document
urlcolor: blue
toc: TRUE
header-includes:
    - \usepackage{caption}
bibliography: references_posthoc.bib  
nocite: | 
  @*
---

\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}

```{r setup, include=FALSE}

if(!require('knitr')) install.packages('knitr') 

library('knitr') 

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE)
```

# 1. Introduction

In this appendix, we present a set of supplementary analyses, to test for the effect of additional moderators on parasitoid responses (and related outcomes) to sugar provisioning. These additional moderators are **the use (or absence of use) of insecticides** and **the species richness of plant mixtures used as nectar sources**. These are conducted as posthoc analyses: we use the models that were already fitted in the initial analysis (see *complete_analysis.Rmd*), and extend them by adding new moderators. We chose to proceed this way for different reasons:

-   First, these analyses were requested during the peer review process, and were therefore not defined during our initial hypothesis framework. To ensure methodological consistency, but also transparency - in particular, to avoid questionable practices such as **HARKing** (*Hypothesis after Results are Known*, Fraser et al. 2018) - it seemed justified to treat these analyses as additional exploratory analyses that were decided *a posteriori.*

-   Second, as we will see below, thse analyses could only be made using a subset of the initial dataset, either because of a lack of data (many unreported cases), or because of the scope of the moderator itself (species richness concerns nectar studies only, and not studies using artificial sugars as a treatment). Thus, just adding these moderators to initial models would have led to a loss of useful information.

-   Finally, as we will also see below, many of these analyses are associated with low sample size, poor model fit, and/or weak signal detection that require cautious interpretation. Presenting them as additional analyses allows us to clearly emphasize their preliminary and exploratory nature.

The following document is a step-by-step guide showing how these posthoc analyses were made, and their results. As you will see, the general procedure is always the same for a given response :

-   We use the models already fitted in the initial analysis (*complete_analysis.Rmd*),refitted on the relevant data subset, as a 'null' reference model.

-   To test for the effect of a desired moderator, we add it as a fixed effect to the null model.

-   We then apply a series of test (significance testing, AIC comparison, diagnostic plots) to evaluate the relevance of adding this moderator to the model - and thus, test if it has an effect on the response.

Finally, note that for clarity, the figures and tables generated in this document are named following a different nomenclature than in the previous supplementary files: these will be referred to as `Fig. SPX` or `Table SPX`, with `P` standing for '*posthoc*'.

*(PS: to reduce the document, we do not show code chunks as in supp. mat. 2 in the output `.pdf`, but these can be found in the original `posthoc_analyses.Rmd` document. A new `.pdf` can also be generated by setting `echo = TRUE` in the setup section.)*

# 2. Preparation

We prepare the analysis by loading the 'clean' version of the data used for the meta-analysis, with effect sizes already computed: see `R/main_script.R` and `complete_analysis.Rmd`.

```{r Initiation}

rm(list = ls())

# Load pacman
if(!require('pacman')) { 
  install.packages('pacman') 
  library('pacman') 
} 

# Load packages
pacman::p_load(
    # Data manipulation
  tidyverse, 
    # Meta-analysis
  metafor, orchaRd, 
    # Graphics
  ggpubr
  )

# Load meta.tab: cf R/main_script.R and complete_analysis.Rmd
meta.tab <- read_rds('Outputs/meta_tab.rds')

# Load custom functions
source('R/Functions/vcovQuick.R') 
  # To re-evaluate variance-covariance matrices on data subsets
source('R/Functions/diagQuick.R')
  # To quickly made diagnostic plots
source('R/Functions/nonLinBubPlot.R')
  # To plot predictions from non-linear models

```

# 3. Insecticides

## 3.1 Data availability

Let's start by testing for the effect of insecticide use on outcome responses to sugar provisioning. First, we evaluate for the availability of data in the dataset, for each outcome variable. As you can see, we have many `Unreported` (we do not know if insecticides or not) or `Unclear` cases (we only have partial information: e.g. synthetic insecticides were not used but we do not know if organic insecticides were used or not). Please refer to the original data and metadata on the repository for more information ([link](https://osf.io/uk765/files/osfstorage)).

```{r Insecticide - availability}

meta.tab %>% 
  group_by(Insecticides, Variable) %>%
  count %>%
  pivot_wider(names_from = Variable, values_from = n) %>%
  dplyr::select(Parasitoid_abundance, Parasitism_rate, Pest_density, Yield) %>%
  kable(caption = "Table SP1. Number of effect sizes corresponding to experiments were insecticide use was clearly reported ('Yes' and 'No', respectively), unclearly reported ('Unclear'), or not reported at all ('Unreported').")

```

Below is a filtered version of the same table, showing only unambiguous cases. As you can see, the data is quite unbalanced between treatments (most experiments with unambiguous reporting do not use insecticides).

```{r Insecticide - availability filtered}

meta.tab.ins <- 
  meta.tab %>%
  filter(Insecticides %in% c('Yes', 'No'))

  # Still very unbalanced though
meta.tab.ins %>% 
  group_by(Insecticides, Variable) %>%
  count %>%
  pivot_wider(names_from = Variable, values_from = n) %>%
  dplyr::select(Parasitoid_abundance, Parasitism_rate, Pest_density, Yield) %>%
  kable(caption = "Table SP2. Number of effect sizes corresponding to experiments were insecticide use was clearly reported (either 'Yes' or 'No'), for each outcome variable.")
```

## 3.2 Fitting models

Now, we will fit models incorporating insecticide use (coded as a binary variable : 'Yes' or 'No') as a new moderator. We will use the general procedure described in the introduction. Let us start with parasitoid abundance. For this first posthoc analysis, each step will be detailed ; we will be more elusive in the next sections, as the general procedure will be the same.

### 3.2.1 Parasitoid abundance

```{r Insecticide - parasitoid abundance subset}
meta.tab.ins.parAb <- meta.tab.ins %>%
  filter(Variable == 'Parasitoid_abundance')
```

#### 3.2.1.1 Meta-analysis on mean

First things first, we fit the reference model for mean parasitoid abundance (see `main_script.R` and `complete_analysis.Rmd`). Second, we re-fit it on the data subset were we have information about insecticide use (see `Table SP2 in`[3.1 Data availability]). This will be our 'null' model. Third, we update this model with an additional moderator on insecticide use (let's call it the 'insecticide' model).

```{r Insecticide - parasitoid abundance mean - model fitting}
  # First we load the model
mod_parAb_mean <- read_rds('Outputs/Models/mod_parAb_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parab_ins <- vcovQuick('lnRR', meta.tab.ins.parAb) 
mod_parAb_mean_ins_null <- 
  update(mod_parAb_mean, data = meta.tab.ins.parAb, V = vcov_parab_ins)

  # We fit the same model with a moderator
mod_parAb_mean_ins_mod <- update(mod_parAb_mean_ins_null,  ~ . + Insecticides)
```

We can then compare these models by a) testing for the significance of moderators and b) comparing AIC values. As you can see below, we see that:

-   the model does not detect for an effect of insecticide use on mean parasitoid abundance (`InsecticideYes treatment`). The overall effect (`intrcpt`) remains significant however.

-   the model including information about insecticide use does not lead to a reduction in AIC (we can then question the relevance of having this moderator in the model).

```{r Insecticide - parasitoid abundance mean - model comparison}

  # Then we compare both models
mod_parAb_mean_ins_mod # No significance
AIC(mod_parAb_mean_ins_null, mod_parAb_mean_ins_mod) # No AIC reduction
```

Finally, we can plot for the distribution of effect sizes according to this moderator just below. We see indeed that no clear difference is detectable. It is likely that the weak amount of data in the 'Yes' treatment (insecticides used) prevents the detection of such an effect, even if it exists.

```{r Insecticide - parasitoid abundance mean - outputs, fig.cap = "Figure SP1. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on mean parasitoid abundance (lnRR)."}

  # Plot
orchaRd::orchard_plot(mod_parAb_mean_ins_mod, xlab = "lnRR", group = "Exp_ID", mod = "Insecticides")
```

On the following diagnostic plots, we can see however that model fit was quite poor, which should make us cautious about their interpretation.

```{r Insecticide - parasitoid abundance mean - diagnostics}
  # Diagnostics
diagQuick(mod_parAb_mean_ins_mod,
          'Parasitoid abundance mean meta-analysis (lnRR) 
          according to insecticide use')
  # note: same conclusion on mod_parAb_mean_ins_null
```

#### 3.2.1.2 Meta-analysis on variation

Now, we repeat the whole procedure, but for the meta-analysis of variance. This time, we will not detail the whole process, all outputs can be found below.

Again, we find no clear sign that there might be an effect of insecticide usage on parasitoid abundance variance. *p-values* associated with estimates do not show any clear trend. - although Fig. SP2 might suggest that when insecticides are used, sugar provisioning leads to a decrease in the variance of parasitoid numbers, while it is not the case when insecticides are not used. Besides, the reduction in AIC brought by the incremented model is very small, meaning that not much knowledge is brought by information on insecticide usage. Finally, model fit is still very poor.

```{r Insecticide - parasitoid abundance variation - model fitting}
  # First we load the model
mod_parAb_var <- read_rds('Outputs/Models/mod_parAb_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parab_ins <- vcovQuick('lnCVR', meta.tab.ins.parAb) 
mod_parAb_var_ins_null <- 
  update(mod_parAb_var, data = meta.tab.ins.parAb, V = vcov_parab_ins)

  # We fit the same model with a moderator
mod_parAb_var_ins_mod <- update(mod_parAb_var_ins_null, ~ . + Insecticides)
```

```{r Insecticide - parasitoid abundance variation - model comparison}

  # Then we compare both models
mod_parAb_var_ins_mod # No detected effect
AIC(mod_parAb_var_ins_null, mod_parAb_var_ins_mod) # Small AIC reduction
```

orchaRd::orchard_plot(mod_parAb_var_ins_mod, xlab = "lnCVR", group = "Exp_ID", mod = "Insecticides")

```{r Insecticide - parasitoid abundance variation - outputs, fig.cap = "Figure SP2. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on the variation of parasitoid abundance (lnCVR)."}

  # Plot
orchaRd::orchard_plot(mod_parAb_var_ins_mod, xlab = "lnCVR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - parasitoid abundance variation - diagnostics}
  # Diagnostics
diagQuick(mod_parAb_var_ins_mod,
          'Parasitoid abundance variation meta-analysis (lnCVR) 
          according to insecticide use')
  # Bad!!
```

### 3.2.2 Parasitism rate

Let us now repeat the analysis for parasitism rate.

```{r Insecticide - parasitism rate subset}
meta.tab.ins.parR <- meta.tab.ins %>%
  filter(Variable == 'Parasitism_rate')
```

#### 3.2.2.1 Meta-analysis on mean

We detect no effect of insecticide usage on the overall effect of sugar provisioning on parasitoid mean (no significant effect detected, no AIC reduction in the incremented model, see also Fig. S3). According to the new model, this overall effect stays positive, but does not depend on insecticides. The model fit is still very poor.

```{r Insecticide - Parasitism rate mean - model fitting}
  # First we load the model
mod_parR_mean <- read_rds('Outputs/Models/mod_parR_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parR_ins <- vcovQuick('lnRR', meta.tab.ins.parR) 
mod_parR_mean_ins_null <- 
  update(mod_parR_mean, data = meta.tab.ins.parR, V = vcov_parR_ins)

  # We fit the same model with a moderator
mod_parR_mean_ins_mod <- update(mod_parR_mean_ins_null,  ~ . + Insecticides)
```

```{r Insecticide - Parasitism rate mean - model comparison}

  # Then we compare both models
mod_parR_mean_ins_mod # No effect detected
AIC(mod_parR_mean_ins_null, mod_parR_mean_ins_mod) # Small AIC reduction
```

```{r Insecticide - Parasitism rate mean - outputs, fig.cap = "Figure SP3. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on mean Parasitism rate (lnRR)."}

  # Plot
orchaRd::orchard_plot(mod_parR_mean_ins_mod, xlab = "lnRR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - Parasitism rate mean - diagnostics}
  # Diagnostics
diagQuick(mod_parR_mean_ins_mod,
          'Parasitism rate mean meta-analysis (lnRR) 
          according to insecticide use')
  # Bad
```

#### 3.2.2.2 Meta-analysis on variation

As for mean, we detect no effect of insecticide usage on the overall effect of sugar provisioning on parasitoid variation (no significant effect detected, no substantial AIC reduction in the incremented model, see also Fig. S4). According to the new model, this overall effect stays negative, but does not depend on insecticides. The model fit is bad here as well.

```{r Insecticide - Parasitism rate variation - model fitting}
  # First we load the model
mod_parR_var <- read_rds('Outputs/Models/mod_parR_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parR_ins <- vcovQuick('lnCVR', meta.tab.ins.parR) 
mod_parR_var_ins_null <- 
  update(mod_parR_var, data = meta.tab.ins.parR, V = vcov_parR_ins)

  # We fit the same model with a moderator
mod_parR_var_ins_mod <- update(mod_parR_var_ins_null,  ~ . + Insecticides)
```

```{r Insecticide - Parasitism rate variation - model comparison}

  # Then we compare both models
mod_parR_var_ins_mod # Sgnificant effect?
AIC(mod_parR_var_ins_null, mod_parR_var_ins_mod) # Small AIC reduction
```

```{r Insecticide - Parasitism rate variation - outputs, fig.cap = "Figure SP4. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on the variation of parasitism rate (lnCVR)."}

  # Plot
orchaRd::orchard_plot(mod_parR_var_ins_mod, xlab = "lnCVR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - Parasitism rate variation - diagnostics}
  # Diagnostics
diagQuick(mod_parR_var_ins_mod,
          'Parasitism rate variation meta-analysis (lnCVR) 
          according to insecticide use')
  # Bad
```

### 3.2.3 Pest density

Let us now repeat the analysis for Pest density.

```{r Insecticide - Pest density subset}
meta.tab.ins.pD <- meta.tab.ins %>%
  filter(Variable == 'Pest_density')
```

#### 3.2.3.1 Meta-analysis on mean

We detect no effect of insecticide usage on the overall effect of sugar provisioning on pest density mean (no significant effect detected, no substantial AIC reduction in the incremented model, see also Fig. S5). We still detect no overall effect, and this does not seem to depend on insecticides. The model fit is still very poor (cf diagnostic plots).

```{r Insecticide - Pest density mean - model fitting}
  # First we load the model
mod_pD_mean <- read_rds('Outputs/Models/mod_pD_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_pD_ins <- vcovQuick('lnRR', meta.tab.ins.pD) 
mod_pD_mean_ins_null <- 
  update(mod_pD_mean, data = meta.tab.ins.pD, V = vcov_pD_ins)

  # We fit the same model with a moderator
mod_pD_mean_ins_mod <- update(mod_pD_mean_ins_null,  ~ . + Insecticides)
```

```{r Insecticide - Pest density mean - model comparison}

  # Then we compare both models
mod_pD_mean_ins_mod # No effect detected
AIC(mod_pD_mean_ins_null, mod_pD_mean_ins_mod) # Small AIC reduction
```

```{r Insecticide - Pest density mean - outputs, fig.cap = "Figure SP5. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on mean Pest density (lnRR)."}

  # Plot
orchaRd::orchard_plot(mod_pD_mean_ins_mod, xlab = "lnRR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - Pest density mean - diagnostics}
diagQuick(mod_pD_mean_ins_mod, 'Pest density mean meta-analysis (lnRR)
          according to insecticide use') # Wow bad
```

#### 3.2.3.2 Meta-analysis on variation

We detect no effect of insecticide usage on the overall effect of sugar provisioning on pest density variation (no significant effect detected, no substantial AIC reduction in the incremented model, see also Fig. S6). We still detect no overall effect, and this does not seem to depend on insecticides.

```{r Insecticide - Pest density variation - model fitting}
  # First we load the model
mod_pD_var <- read_rds('Outputs/Models/mod_pD_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_pD_ins <- vcovQuick('lnCVR', meta.tab.ins.pD) 
mod_pD_var_ins_null <- 
  update(mod_pD_var, data = meta.tab.ins.pD, V = vcov_pD_ins)

  # We fit the same model with a moderator
mod_pD_var_ins_mod <- update(mod_pD_var_ins_null,  ~ . + Insecticides)
```

```{r Insecticide - Pest density variation - model comparison}

  # Then we compare both models
mod_pD_var_ins_mod # No effect detected
AIC(mod_pD_var_ins_null, mod_pD_var_ins_mod) # Small AIC reduction
```

```{r Insecticide - Pest density variation - outputs, fig.cap = "Figure SP5. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on the variation of pest density (lnCVR)."}

  # Plot
orchaRd::orchard_plot(mod_pD_var_ins_mod, xlab = "lnCVR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - Pest density variation - diagnostics}
diagQuick(mod_pD_var_ins_mod, 'Pest density variation meta-analysis (lnCVR)
          according to insecticide use') 

# Meh
```

### 3.2.4 Yield

Let us now repeat the analysis for Yield.

```{r Insecticide - Yield subset}
meta.tab.ins.yield <- meta.tab.ins %>%
  filter(Variable == 'Yield')
```

#### 3.2.4.1 Meta-analysis on mean

Regarding yield, the model seems to indicate that the overall effect of sugar provisioning depends on insecticides: we get a positive effect on mean yield when no insecticides are used, but not when they are (significant effect suggested by the model, see Fig. S7). However, model fit is exceptionally poor and we see no decrease in AIC.

```{r Insecticide - Yield mean - model fitting}
  # First we load the model
mod_yield_mean <- read_rds('Outputs/Models/mod_yield_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_yield_ins <- vcovQuick('lnRR', meta.tab.ins.yield) 
mod_yield_mean_ins_null <- 
  update(mod_yield_mean, data = meta.tab.ins.yield, V = vcov_yield_ins)

  # We fit the same model with a moderator
mod_yield_mean_ins_mod <- update(mod_yield_mean_ins_null,  ~ . + Insecticides)
```

```{r Insecticide - Yield mean - model comparison}

  # Then we compare both models
mod_yield_mean_ins_mod # Small effect
AIC(mod_yield_mean_ins_null, mod_yield_mean_ins_mod) # No AIC reduction
```

```{r Insecticide - Yield mean - outputs, fig.cap = "Figure SP7. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on mean yield (lnRR)."}

  # Plot
orchaRd::orchard_plot(mod_yield_mean_ins_mod, xlab = "lnRR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - Yield mean - diagnostics}
  # Diagnostics
diagQuick(mod_yield_mean_ins_mod,
          'Yield mean meta-analysis (lnRR) 
          according to insecticide use')
  # Bad
```

#### 3.2.4.2 Meta-analysis on variation

The new model also seems to indicate that the overall effect of sugar provisioning on yield variation depends on insecticides. Apparently, sugar provisioning decreases more yield variation when insecticides are used (see also Fig. SP8). However, we see no clear trend, as confidence intervals cross zero for each level of the moderator (Fig. SP8) - see also the very low sample size (with only two experiments where experiments are used).

```{r Insecticide - Yield variation - model fitting}
  # First we load the model
mod_yield_var <- read_rds('Outputs/Models/mod_yield_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_yield_ins <- vcovQuick('lnCVR', meta.tab.ins.yield) 
mod_yield_var_ins_null <- 
  update(mod_yield_var, data = meta.tab.ins.yield, V = vcov_yield_ins)

  # We fit the same model with a moderator
mod_yield_var_ins_mod <- update(mod_yield_var_ins_null,  ~ . + Insecticides)
```

```{r Insecticide - Yield variation - model comparison}

  # Then we compare both models
mod_yield_var_ins_mod # Significant effect?
AIC(mod_yield_var_ins_null, mod_yield_var_ins_mod) # Small AIC reduction
```

```{r Insecticide - Yield variation - outputs, fig.cap = "Figure SP8. Meta-analysis of the influence of Insecticide use ('Yes' or 'No') on the effect size of sugar provisioning on yield variation (lnCVR)."}

  # Plot
orchaRd::orchard_plot(mod_yield_var_ins_mod, xlab = "lnCVR", group = "Exp_ID", mod = "Insecticides")
```

```{r Insecticide - Yield variation - diagnostics}
  # Diagnostics
diagQuick(mod_yield_var_ins_mod,
          'Yield variation meta-analysis (lnCVR) 
          according to insecticide use')
  # Bad
```

## 3.3 Conclusions on insecticide usage

Unfortunately, this analysis leaves us with no clear results. Overall, sample sizes are very low (in some models and for some moderator levels, only two experiments are represented), which often leads to very poor model fit. Besides, if we rely on information theory criteria (AIC), it seems that given the available data, we mostly cannot say than knowledge about insecticide usage improves our understanding of the effects of sugar provisioning on parasitoid-related outcomes.

Some significance tests and visual exploration of effect sizes, however, indicate some trends that are worth investigating for future studies, notably regarding effects on **crop yield**. Indeed, using no insecticides may allow sugar provisioning to increase yields, while using them erases this putative effect. But as highlighted, given the poor model fit and lack of data, we cannot bring definitive conclusions to these questions and may only encourage the scientific community to conduct new experiments to evaluate such effects and/or clear reporting of insecticide usage in future studies.

# 4. Nectar plant species richness

## 4.1 Data availability {data-link="3.1 Data availability"}

Let us now test for the effect of nectar plant diversity (approximated here as the species richness of plants in mixtures used for sugar provisioning) on sugar supplementation outcomes. Again, we can start by looking for the availability of data in the dataset, for each outcome variable.

```{r Nectar plant richness - availability}

meta.tab %>% 
  group_by(Nectar_providing_plants_diversity, Variable) %>%
  count %>%
  pivot_wider(names_from = Variable, values_from = n) %>%
  dplyr::select(Parasitoid_abundance, Parasitism_rate, Pest_density, Yield) %>%
  mutate(n_pl = as.numeric(Nectar_providing_plants_diversity)) %>%
  arrange(n_pl) %>%
  dplyr::select(n_pl, everything()) %>%
  dplyr::select(-n_pl) %>%
    rename('Number of plant species' = Nectar_providing_plants_diversity) %>%
  kable(caption = "Table SP3. Number of effect sizes available for each level of nectar plant richness in sugar supplementation experiments (total number of plant species used).")
```

Note that a) we have six '`Unreported`' cases (these correspond to cases when spontaneous vegetation was used as a treatment, but we do not know how many different species - two papers, Bone et al. 2009 and Sann et al. 2018) and b) we have 35 `NA` that correspond to studies were artificial sugars were used as a food source.

See also that data availability is very unbalanced across nectar plant diversity levels. Most studies actually use only one plant species as a potential food source.

```{r Nectar plant richness - mono vs plurispecific studies}
  meta.tab %>% 
  group_by(Nectar_providing_plants_diversity, Variable) %>%
  count %>%
  pivot_wider(names_from = Variable, values_from = n) %>%
  dplyr::select(Parasitoid_abundance, Parasitism_rate, Pest_density, Yield) %>%
  mutate(n_pl = as.numeric(Nectar_providing_plants_diversity)) %>%
  arrange(n_pl) %>%
  dplyr::select(n_pl, everything()) %>%
  filter(!is.na(Nectar_providing_plants_diversity)) %>% # these correspond to AS treatments
  ungroup %>%
  dplyr::select(-Nectar_providing_plants_diversity) %>%
  mutate(n_pl_categ = ifelse(n_pl > 1 | is.na(n_pl), '>1', 1)) %>%
  group_by(n_pl_categ) %>%
  summarise(across(c(Parasitoid_abundance, Parasitism_rate, Pest_density, Yield), ~sum(.x, na.rm = T))) %>%
    rename('Number of plant species' = n_pl_categ) %>%
  kable(caption = "Table SP3. Number of effect sizes available for each level of nectar plant richness in sugar supplementation experiments (one or more).")
```

## 4.2 Fitting models

```{r Nectar plant richness - table preparation}
meta.tab.div <- 
  meta.tab %>% 
  mutate(n_pl = as.numeric(Nectar_providing_plants_diversity)) %>% 
  filter(!is.na(n_pl))
```

Now, we will fit models incorporating nectar plant species richness (coded as a continuous variable reflecting the number of species) as a new moderator. Again, we will use the general procedure described in the introduction (see also section [3.2.1 Parasitoid abundance] on insecticde effects for a detailed guide). However, in that case, we do not expect all effects to be linear (see *e.g.* Albrecht et al. 2020). Thus, we will fit polynomial models to allow for quadratic effects of plant species richness on the outcomes of sugar provisioning. (Albrecht et al. 2020). Let us start with parasitoid abundance.

### 4.2.1 Parasitoid abundance

```{r Nectar plant richness - Parasitoid abundance subset}

  # Extracting the data
meta.tab.div.parAb <- meta.tab.div %>%
  filter(Variable == 'Parasitoid_abundance')
```

#### 4.2.1.1 Meta-analysis on mean

As you can see below, we find no sign for an influence of nectar plant species richness on the effect of sugar provisioning on mean parasitoid abundance. *p-values* associated with estimates do not suggest effects, we get no AIC reduction, and the plot shows a quasi-linear trend (Fig. SP9). Note however that the model fit is still quite poor (diagnostic plots).

```{r Nectar plant richness - Parasitoid abundance mean - model fitting}
  # First we load the model
mod_parAb_mean <- read_rds('Outputs/Models/mod_parAb_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parAb_div <- vcovQuick('lnRR', meta.tab.div.parAb) 
mod_parAb_mean_div_null <- 
  update(mod_parAb_mean, data = meta.tab.div.parAb, V = vcov_parAb_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_parAb_mean_div_mod <- update(mod_parAb_mean_div_null, 
                                  ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Parasitoid abundance mean - model comparison}

  # Then we compare both models
mod_parAb_mean_div_mod # No effect detected
AIC(mod_parAb_mean_div_null, mod_parAb_mean_div_mod) # No AIC reduction
```

```{r Nectar plant richness - Parasitoid abundance mean - outputs, fig.cap = "Figure SP9. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on mean parasitoid abundance (lnRR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_parAb_mean_div_mod,
              moderator = 'n_pl',
              es = 'lnRR',
              xlab = 'Nectar plant species richness',
              resp = 'Parasitoid abundance')
```

```{r Nectar plant richness - Parasitoid abundance mean - diagnostics}
  # Diagnostics
diagQuick(mod_parAb_mean_div_mod,
          'Parasitoid abundance mean meta-analysis (lnRR) 
          according to nectar plant species richness')
  # Bad
```

#### 4.2.1.2 Meta-analysis on variation

As for mean, we find no sign for an influence of nectar plant species richness on the effect of sugar provisioning on parasitoid abundance variation. *p-values* associated with estimates do not suggest effects, we get no substantial AIC reduction, and the plot does not show any clear trend (Fig. SP10) - especially when considering confidence and prediction intervals. Model fit is better this time!

```{r Nectar plant richness - Parasitoid abundance variation - model fitting}
  # First we load the model
mod_parAb_var <- read_rds('Outputs/Models/mod_parAb_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parAb_div <- vcovQuick('lnCVR', meta.tab.div.parAb) 
mod_parAb_var_div_null <- 
  update(mod_parAb_var, data = meta.tab.div.parAb, V = vcov_parAb_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_parAb_var_div_mod <- update(mod_parAb_var_div_null, 
                                 ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Parasitoid abundance variation - model comparison}

  # Then we compare both models
mod_parAb_var_div_mod # No effect detected
AIC(mod_parAb_var_div_null, mod_parAb_var_div_mod) # Very small AIC reduction
```

```{r Nectar plant richness - Parasitoid abundance variation - outputs, fig.cap = "Figure SP10. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on var parasitoid abundance (lnCVR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_parAb_var_div_mod,
              moderator = 'n_pl',
              es = 'lnCVR',
              xlab = 'Nectar plant species richness',
              resp = 'Parasitoid abundance')
```

```{r Nectar plant richness - Parasitoid abundance variation - diagnostics}
  # Diagnostics
diagQuick(mod_parAb_var_div_mod,
          'Parasitoid abundance variation meta-analysis (lnCVR) 
          according to nectar plant species richness')
  # Bad
```

### 4.2.2 Parasitism rate

```{r Nectar plant richness - Parasitism rate subset}

  # Extracting the data
meta.tab.div.parR <- meta.tab.div %>%
  filter(Variable == 'Parasitism_rate')
```

#### 4.2.2.1 Meta-analysis on mean

Same overall conclusion. We get a small reduction in AIC when incorporating nectar plant species richness as moderator, but *p-values* associated with estimates do not suggest any effects, nether do Fig. SP11.

```{r Nectar plant richness - Parasitism rate mean - model fitting}
  # First we load the model
mod_parR_mean <- read_rds('Outputs/Models/mod_parR_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parR_div <- vcovQuick('lnRR', meta.tab.div.parR) 
mod_parR_mean_div_null <- 
  update(mod_parR_mean, data = meta.tab.div.parR, V = vcov_parR_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_parR_mean_div_mod <- update(mod_parR_mean_div_null, 
                                  ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Parasitism rate mean - model comparison}

  # Then we compare both models
mod_parR_mean_div_mod # No effect detected
AIC(mod_parR_mean_div_null, mod_parR_mean_div_mod) # Small AIC reduction
```

```{r Nectar plant richness - Parasitism rate mean - outputs, fig.cap = "Figure SP11. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on mean Parasitism rate (lnRR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_parR_mean_div_mod,
              moderator = 'n_pl',
              es = 'lnRR',
              xlab = 'Nectar plant species richness',
              resp = 'Parasitism rate')
```

```{r Nectar plant richness - Parasitism rate mean - diagnostics}
  # Diagnostics
diagQuick(mod_parR_mean_div_mod,
          'Parasitism rate mean meta-analysis (lnRR) 
          according to nectar plant species richness')
  # Bad
```

#### 4.2.2.2 Meta-analysis on variation

As for mean, we find no sign for an influence of nectar plant species richness on the effect of sugar provisioning on Parasitism rate variation : no *p-values* under the significance threshold, no AIC reduction,a quasi-linear relationship (Fig. SP12). Model fit is also quite poor (Fig. SP12).

```{r Nectar plant richness - Parasitism rate variation - model fitting}
  # First we load the model
mod_parR_var <- read_rds('Outputs/Models/mod_parR_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_parR_div <- vcovQuick('lnCVR', meta.tab.div.parR) 
mod_parR_var_div_null <- 
  update(mod_parR_var, data = meta.tab.div.parR, V = vcov_parR_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_parR_var_div_mod <- update(mod_parR_var_div_null, 
                                 ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Parasitism rate variation - model comparison}

  # Then we compare both models
mod_parR_var_div_mod # No effect detected
AIC(mod_parR_var_div_null, mod_parR_var_div_mod) # No AIC reduction
```

```{r Nectar plant richness - Parasitism rate variation - outputs, fig.cap = "Figure SP12. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on var Parasitism rate (lnCVR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_parR_var_div_mod,
              moderator = 'n_pl',
              es = 'lnCVR',
              xlab = 'Nectar plant species richness',
              resp = 'Parasitism rate')
```

```{r Nectar plant richness - Parasitism rate variation - diagnostics}
  # Diagnostics
diagQuick(mod_parR_var_div_mod,
          'Parasitism rate variation meta-analysis (lnCVR) 
          according to nectar plant species richness')
  # Bad
```

### 4.2.3 Pest density

```{r Nectar plant richness - Pest density subset}

  # Extracting the data
meta.tab.div.pD <- meta.tab.div %>%
  filter(Variable == 'Pest_density')
```

#### 4.2.3.1 Meta-analysis on mean

Same overall conclusion than in other analyses. No substantial reduction in AIC, no significant *p-values*, a quasi-linear relationship (Fig. SP13).

```{r Nectar plant richness - Pest density mean - model fitting}
  # First we load the model
mod_pD_mean <- read_rds('Outputs/Models/mod_pD_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_pD_div <- vcovQuick('lnRR', meta.tab.div.pD) 
mod_pD_mean_div_null <- 
  update(mod_pD_mean, data = meta.tab.div.pD, V = vcov_pD_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_pD_mean_div_mod <- update(mod_pD_mean_div_null, 
                                  ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Pest density mean - model comparison}

  # Then we compare both models
mod_pD_mean_div_mod # No effect detected
AIC(mod_pD_mean_div_null, mod_pD_mean_div_mod) # Small AIC reduction
```

```{r Nectar plant richness - Pest density mean - outputs, fig.cap = "Figure SP13. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on mean Pest density (lnRR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_pD_mean_div_mod,
              moderator = 'n_pl',
              es = 'lnRR',
              xlab = 'Nectar plant species richness',
              resp = 'Pest density')
```

```{r Nectar plant richness - Pest density mean - diagnostics}
  # Diagnostics
diagQuick(mod_pD_mean_div_mod,
          'Pest density mean meta-analysis (lnRR) 
          according to nectar plant species richness')
```

#### 4.2.3.2 Meta-analysis on variation

Fig. SP14 might indicate a trend here, but we find no quantitative sign for an influence of nectar plant species richness on the effect of sugar provisioning on pest density variation : no *p-values* under the significance threshold, no AIC reduction.

```{r Nectar plant richness - Pest density variation - model fitting}
  # First we load the model
mod_pD_var <- read_rds('Outputs/Models/mod_pD_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_pD_div <- vcovQuick('lnCVR', meta.tab.div.pD) 
mod_pD_var_div_null <- 
  update(mod_pD_var, data = meta.tab.div.pD, V = vcov_pD_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_pD_var_div_mod <- update(mod_pD_var_div_null, 
                                 ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Pest density variation - model comparison}

  # Then we compare both models
mod_pD_var_div_mod # No effect detected
AIC(mod_pD_var_div_null, mod_pD_var_div_mod) # No AIC reduction
```

```{r Nectar plant richness - Pest density variation - outputs, fig.cap = "Figure SP14. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on var Pest density (lnCVR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_pD_var_div_mod,
              moderator = 'n_pl',
              es = 'lnCVR',
              xlab = 'Nectar plant species richness',
              resp = 'Pest density')
```

```{r Nectar plant richness - Pest density variation - diagnostics}
  # Diagnostics
diagQuick(mod_pD_var_div_mod,
          'Pest density variation meta-analysis (lnCVR) 
          according to nectar plant species richness')
```

### 4.2.4 Yield

```{r Nectar plant richness - Yield subset}

  # Extracting the data
meta.tab.div.yield <- meta.tab.div %>%
  filter(Variable == 'Yield')
```

#### 4.2.4.1 Meta-analysis on mean

Same overall conclusion than for other variables: no sign for an effect. *p-values* associated with estimates do not suggest any effect, no substantial AIC reduction, no clear trend on Fig. SP15. See also the very low sample size and poor model fit.

```{r Nectar plant richness - Yield mean - model fitting}
  # First we load the model
mod_yield_mean <- read_rds('Outputs/Models/mod_yield_mean.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_yield_div <- vcovQuick('lnRR', meta.tab.div.yield) 
mod_yield_mean_div_null <- 
  update(mod_yield_mean, data = meta.tab.div.yield, V = vcov_yield_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_yield_mean_div_mod <- update(mod_yield_mean_div_null, 
                                  ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Yield mean - model comparison}

  # Then we compare both models
mod_yield_mean_div_mod # No effect detected
AIC(mod_yield_mean_div_null, mod_yield_mean_div_mod) # No AIC reduction
```

```{r Nectar plant richness - Yield mean - outputs, fig.cap = "Figure SP15. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on mean Yield (lnRR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_yield_mean_div_mod,
              moderator = 'n_pl',
              es = 'lnRR',
              xlab = 'Nectar plant species richness',
              resp = 'Yield')
```

```{r Nectar plant richness - Yield mean - diagnostics}
  # Diagnostics
diagQuick(mod_yield_mean_div_mod,
          'Yield mean meta-analysis (lnRR) 
          according to nectar plant species richness')
```

#### 4.2.4.2 Meta-analysis on variation

Here, visual representation might suggest a linear trend (Fig. s16), and we get a small AIC reduction in the model containing the moderator, but confidence intervals are huge and we get no definitive sign for a clear effect if we look at estimates and their *p-values*. Again, sample size probably does not help here.

```{r Nectar plant richness - Yield variation - model fitting}
  # First we load the model
mod_yield_var <- read_rds('Outputs/Models/mod_yield_var.rds')

  # Then, we re-fit the final 'null' model on the data subset
vcov_yield_div <- vcovQuick('lnCVR', meta.tab.div.yield) 
mod_yield_var_div_null <- 
  update(mod_yield_var, data = meta.tab.div.yield, V = vcov_yield_div)

# We fit the same model with n. plant species as a moderator
  # Allowing quadratic relationships
mod_yield_var_div_mod <- update(mod_yield_var_div_null, 
                                 ~ . + poly(n_pl, 2))
```

```{r Nectar plant richness - Yield variation - model comparison}

  # Then we compare both models
mod_yield_var_div_mod # No effect detected
AIC(mod_yield_var_div_null, mod_yield_var_div_mod) # Small AIC reduction
```

```{r Nectar plant richness - Yield variation - outputs, fig.cap = "Figure SP12. Meta-analysis of the influence of nectar plant species richness on the effect size of sugar provisioning on var Yield (lnCVR)."}

  # Using custom function nonLinBubPlot()
nonLinBubPlot(model = mod_yield_var_div_mod,
              moderator = 'n_pl',
              es = 'lnCVR',
              xlab = 'Nectar plant species richness',
              resp = 'Yield')
```

```{r Nectar plant richness - Yield variation - diagnostics}
  # Diagnostics
diagQuick(mod_yield_var_div_mod,
          'Yield variation meta-analysis (lnCVR) 
          according to nectar plant species richness')
```

## 4.3 Conclusions on nectar species richness

So far, our investigations do not allow us to conclude for any influence of nectar plant species richness on the effects of sugar provisioning on parasitoid-related outcomes. The data might suggest some trends (*e.g.* a stabilising effect on yield), but in such cases there is clearly not enough of it to draw any solid conclusions. Besides, note one limitation of our approach: we used the number of plants species in the mixtures as a crude estimate of nectar plant diversity, but we are not even always sure that these are all nectar-producing plants (this is not always detailed by authors). Not also that here we do not consider any kind of mechanistic aspects of plant diversity (*e.g.* complementarity in traits/phenology or selection effects) that may lead to diversity-performance relationships.

In the end, we cannot overrule the existence of any effect of richness in plant mixtures, but at this step we see no sign for such effects.

# 5. References
